\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-21 concepts.tex
post-telecon updates to title europa sections

\begin{enumerate}
\item \textbf{Tokens} Temporally scoped entities that correspond to Intervals in the CAIP framework, are used to represent  state and actions in time. A\textbf{Token State model} is defined to support an efficient implementation of plan-space search algorithms.

@@

  \begin{enumerate}
  \item \textit{String}: sequences of characters, like "Red",
    "Spirit", etc

@@

  \begin{enumerate}
  \item \textit{Enumerated}: Finite sets over any data type, specified
    explicitly, for instance: ["Red","Yellow","Green"], [1,18,32], etc
  \item \textit{Interval}: Only for Numeric data types, they are
    specified by a [LowerBound,UpperBound] pair, for instance: [1,10],
    [5.0,100.0], etc.
  \end {enumerate}

@@

\item[\textbf{Tokens}] In first order logic, a predicate defines a
  relation between objects and properties \comment{use Genesereth citation?}.  In
  \eu, we define such relations between variables whose domains are
  sets of objects and sets of properties to describe state and
  behavior. For example, we might use a predicate \texttt{At($a$,$l$)}
  to indicate that agent $a$ is at location $l$, or a predicate
  \texttt{Buy($a$,$p$}) to indicate that agent $a$ is taking acting to
  buy product $p$. Note that $a$ is a variable which may have a number
  of possible values in a problem with multiple agents. Similarly, $l$
  and $p$ are variables whose values are the set of possible positions
  and products respectively. \eu can be used to create partial plans,
  where the domains of variables $a$ and $l$ can have more than one
  possible value in them, or grounded plans, where single values will
  be specified for each variable as we saw in the case of the
  N-queen's problem.

@@

Notice that the \texttt{Own(Drill)} token that represents the goal is
not immediately placed on the \texttt{AgentBag} timeline since \eu
must determine whether it can achieve that goal and how. When the goal
is posted and before any decisions are made on it, the
\texttt{Own(Drill)} token is created in an INACTIVE state, then \eu
looks at the current partial plan and considers 2 alternatives:

@@

\item If there are any tokens in the plan that are compatible with the
  new goal, \eu may attempt to satisfy the goal by merging it with any
  of them (if there is more than one it can try them one at a time),
  in this case, the state of the token would change to MERGED.

@@

As we can see, a token's state can go from INACTIVE to ACTIVE, MERGED
or REJECTED, this lifecycle is illustrated in the figure below.

>>>>

\item \textbf{Tokens} Temporally scoped entities that correspond to
  Intervals in the CAIP framework, are used to represent state and
  actions in time. A\textbf{Token State model} is defined to support
  an efficient implementation of plan-space search algorithms.

@@

  \item \textit{String}: sequences of characters, like "Red",
    "Spirit", etc

@@

  \item \textit{Enumerated}: Finite sets over any data type, specified
    explicitly, for instance: ["Red","Yellow","Green"], [1,18,32], etc

  \item \textit{Interval}: Only for Numeric data types, they are
    specified by a [LowerBound,UpperBound] pair, for instance: [1,10],
    [5.0,100.0], etc.

@@

\item[\textbf{Tokens}] In first order logic, a predicate defines a
  relation between objects and properties \cite{gen87}.  In \eu, we
  define such relations between variables whose domains are sets of
  objects and sets of properties to describe state and behavior. For
  example, we might use a predicate \texttt{At($a$,$l$)} to indicate
  that agent $a$ is at location $l$, or a predicate
  \texttt{Buy($a$,$p$}) to indicate that agent $a$ is taking acting to
  buy product $p$. Note that $a$ is a variable which may have a number
  of possible values in a problem with multiple agents. Similarly, $l$
  and $p$ are variables whose values are the set of possible positions
  and products respectively. \eu can be used to create partial plans,
  where the domains of variables $a$ and $l$ can have more than one
  possible value in them, or grounded plans, where single values will
  be specified for each variable as we saw in the case of the
  N-queen's problem.

@@

  Note that the \texttt{Own(Drill)} token that represents the goal is
  not immediately placed on the \texttt{AgentBag} timeline since \eu
  must determine whether it can achieve that goal and how. When the
  goal is posted and before any decisions are made on it, the
  \texttt{Own(Drill)} token is created in an INACTIVE state, then \eu
  looks at the current partial plan and considers 2 alternatives:

@@

\item If there are any tokens in the plan that are compatible with the
  new goal, \eu may attempt to satisfy the goal by merging it with any
  of them (if there is more than one it can try them one at a time),
  in this case, the state of the token would change to
  \texttt{MERGED}.

@@

As we can see, a token's state can go from \texttt{INACTIVE} to
\texttt{ACTIVE, MERGED} or \texttt{REJECTED}, this lifecycle is
illustrated in the figure below.

### 2012-02-21 setobook.tex
added more latex markup to europa.tex and included europa.tex in setobook.tex
citations added to europa text
post-telecon updates to title europa sections

% \usepackage[agsm]{harvard}

\titlerunning{Towards Deliberative Control of Autonomous Robots}
\authorrunning{K.Rajan et. al.}

\title*{\textbf{\sc Towards Deliberative Control of Autonomous Robots}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \texttt{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \texttt{javier.barreiro@nasa.gov}}

@@

@@

@@

Authors Rajan and Py are funded by a block grant from the David and
Lucile Packard Foundation to MBARI.

>>>>

% \titlerunning{Towards Deliberative Control of Autonomous Robots}
% \authorrunning{K.Rajan et. al.}

\title*{\textbf{\sc Towards Deliberative Control in Marine Robotics}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \emph{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \emph{javier.barreiro@nasa.gov}}

@@

\input{europa-basics.tex}

@@

\input{europa.tex}

@@

Rajan and Py are funded by a block grant from the David and Lucile
Packard Foundation to MBARI. They thank their collaborators J. Ryan,
J. Harvey, R. Vrijenhoek and J. Bellingham at MBARI. In addition they
thank colleagues M. del Alto, D. Korsmeyer and S. Zornetzer at NASA
Ames who made \eu available as open source. The authors are indebted
to N. Muscettola for his ideas and early work at NASA Ames which forms
the basis of this work.
